Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows

### 2023-04-17 outputs/paper/paper.qmd
Commit

---
title: "Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows"
subtitle: "An Analysis of United States, Canada, United Kingdom, Australia, and Japan"
author: 
  - Jenny Shen
thanks: "Code and data are available at: https://github.com/jennyshen-playground/analysis_of_employment_rate_perminant_immigrant_inflows.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper explores the relationship between a country's employment rate and its ability to attract and retain permanent immigrants. Using a linear regression analysis, we examine five countries with relatively high immigration numbers: United States, Canada, United Kingdom, Australia, and Japan from 2008 to 2018. We drawn data  from the OECD website, with a focus on the percentage of the working-age population. These findings matter as they can influence permanent immigrant inflows and guide governments in developing policies to attract and retain permanent immigrants.The rise of employment rate can enhance economic development, and also associates with increased number of permanent immigrants inflow. This suggests that improving employment rate leads to better immigration that generate significant economic and social benefits for a country."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Immigration has been a key driver of economic growth and cultural diversity for countries around the world. Over the past two decades, many countries have opened doors to immigration, recognizing the significant economic and social benefits that immigration can bring. However, immigration policies and their implementation have varied across countries, with some facing challenges in attracting and retaining permanent immigrants. One possible factor that could influence a country’s ability to attract and retain immigrants is its employment rate. High employment rates means that the country has economic stability and job opportunities, making a country a more attractive destination for permanent immigrants. Whereas, low employment rates could signal economic instability, leading to a decrease in permanent immigrant inflows.

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, The estimand here that we’re trying to estimate is the correlation of employment rate and permanent immigrants inflows. Specifically, we will focus on 5 countries with relatively high immigration numbers (United States, Canada, United Kingdom, Australia, and Japan). We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.

@@

@@

# Appendix {-}

>>>>

---
title: "Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows"
subtitle: "An Analysis of United States, Canada, United Kingdom, Australia, and Japan"
author: 
  - Jenny Shen
thanks: "Code and data are available at: https://github.com/jennyshen-playground/analysis_of_employment_rate_perminant_immigrant_inflows.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper explores the relationship between a country's employment rate and its ability to attract and retain permanent immigrants. Using a linear regression analysis, we examine five countries with relatively high immigration numbers: United States, Canada, United Kingdom, Australia, and Japan from 2008 to 2018. We drawn data  from the OECD website, with a focus on the percentage of the working-age population. These findings matter as they can influence permanent immigrant inflows and guide governments in developing policies to attract and retain permanent immigrants.The rise of employment rate can enhance economic development, and also associates with increased number of permanent immigrants inflow. This suggests that improving employment rate leads to better immigration that generate significant economic and social benefits for a country."
number-sections: true
bibliography: references.bib
---

@@

Immigration has been a key driver of economic growth and cultural diversity for countries around the world. Over the past two decades, many countries have opened doors to immigration, recognizing the significant economic and social benefits that immigration can bring. However, immigration policies and their implementation have varied across countries, with some facing challenges in attracting and retaining permanent immigrants. One possible factor that could influence a country's ability to attract and retain immigrants is its employment rate. High employment rates means that the country has economic stability and job opportunities, making a country a more attractive destination for permanent immigrants. Whereas, low employment rates could signal economic instability, leading to a decrease in permanent immigrant inflows.

In this paper, we will examine the relationship between a country's employment rate and permanent immigrant inflows through a linear regression analysis, The estimand here that we're trying to estimate is the correlation of employment rate and permanent immigrants inflows. Specifically, we will focus on 5 countries with relatively high immigration numbers (United States, Canada, United Kingdom, Australia, and Japan). We will draw data from the OECD website. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development.

@@

```{r}
#| include: false
#| warning: false
#| message: false
#| 
#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

permanent_immigrant <- read_csv(here::here("inputs/data/permanent_immigrant_inflows_cleaned.csv"))
employment_rate <- read_csv(here::here("inputs/data/employment_rate_cleaned"))
merged_data <- read_csv(here::here("inputs/data/merged_data"))
```

@@

# Appendix {.unnumbered}
